### 2025-04-27 conteudo/tool/architecture.tex
remove setup and change arc diagram

The Query Responder consumes the Temporary Codebase and the Code Duplication Database to extract duplicated functions-related information per user request.

@@

\begin{figure}
\includegraphics[scale=0.5]{diagrama_mestrado}
\caption{Architecture diagram demonstrating the relationship between the tool components.}
\label{fig:diagram}
\end{figure}

@@

The Code Duplication Finder iterates through every pair of source code files in the temporary codebase, representing 
functions from the input codebase. For each pair of files, we execute a code duplication detection method that computes 
a metric measuring how similar the pair of files is, which we refer to as similarity. 
If the similarity is greater than or equal to the minimum similarity threshold 
(a parameter provided by the user during the Setup step), we store this pair of functions along with its 
similarity in the Code Duplication Database.

@@

The Query Responder step is the component the user executes multiple times to consult information about duplicated functions in a codebase processed by the Setup step. The Query Responder step utilizes the temporary codebase and the Code Duplication Database as inputs to answer the user's request, such as querying the total number of duplicated functions in a specific input codebase or listing duplicated functions above a certain similarity threshold. This component was developed to be extensible, allowing other queries to be easily added. Currently, the Query Responder step supports the following queries:

>>>>

The Query Responder consumes the Temporary Codebase and the Code Duplication Database to extract duplicated 
functions-related information per user request. If the user executes the Query Responder without executing the 
Preprocessor, the Query Responder calls the Preprocessor to create the required artifacts.

@@

\begin{figure}
\includegraphics[scale=0.4]{diagrama_mestrado}
\caption{Architecture diagram demonstrating the relationship between the tool components.}
\label{fig:diagram}
\end{figure}

@@

The Code Duplication Finder iterates through every pair of source code files in the temporary codebase, representing 
functions from the input codebase. For each pair of files, we execute a code duplication detection method that computes 
a metric measuring how similar the pair of files is, which we refer to as similarity. 
If the similarity is greater than or equal to the minimum similarity threshold 
(a parameter provided by the user during the Preprocessor), we store this pair of functions along with its 
similarity in the Code Duplication Database.

@@

The Query Responder step is the component the user executes multiple times to consult information about duplicated functions in a codebase processed by the Preprocessor. The Query Responder step utilizes the temporary codebase and the Code Duplication Database as inputs to answer the user's request, such as querying the total number of duplicated functions in a specific input codebase or listing duplicated functions above a certain similarity threshold. This component was developed to be extensible, allowing other queries to be easily added. Currently, the Query Responder step supports the following queries:
